% CSC311 Machine Learning Challenge write-up

% Preamble
\documentclass{article}
\usepackage{amsmath}

% Title
\title{CSC311 Machine Learning Challenge}
\author{Mars Ponce (poncema2), } % Add your names and UTORids here
\date{April 5 2024, 22:00 EST}



\begin{document}

\maketitle

\newpage

\section*{Requirements}
\begin{itemize}
	\item (2 points) Data: Describe how you explored your data, and the process through which you determined your input features. How did you end up representing your data? What else did you try? (see more in handout.pdf)
	\item (1 points) Model: A Description of the model(s) that you are evaluating/exploring. We are expecting a thorough exploration of at least 3+ family of models, even if you don't utimately use those models. (see more in handout.pdf) 
	\item (4 points) Model Choice and Hyperparameters. How you are determining what model(s) to use in your final \verb|pred.py|, as well as an exploration of hyperparameters. (see more in handout.pdf)
	\item (1 point) Prediction: How well do would you expect your model to perform on the test set? (see more in handout.pdf)
	\item Workload Distribution: A description of what each person in the group contributed to the project. A 1-2 sentence description of each person’s role is sufficient. Each student’s description must be written by that student in order for them to receive credit for the project.
\end{itemize}

\section{Data}

\section{Model}

\section{Model Choice and Hyperparameters}

\section{Prediction}

\section{Workload Distribution}

\end{document}
